---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


# seal.econum - import, validate and analyse seal AA3 data file

## Guyliann Engels & Raphael Conotte

[![Travis-CI Build Status](https://travis-ci.com/EcoNum/seal.econum.svg?branch=master)](https://travis-ci.com/EcoNum/seal.econum)
[![License](https://img.shields.io/badge/license-GPL-blue.svg)](https://www.gnu.org/licenses/gpl-2.0.html)

## Overview

seal.econum includes several functions to import, validate and analyse seal AA3 data file.

## Installation

### Latest stable version

The latest stable version of seal.econum can simply be installed from github with the last releases :

```{r}
# TODO
```


### Development version

Use install_github() to install the seal.econum package from Github (source from master branch will be recompiled on your machine):

```{r, eval = FALSE}
# install.packages("remotes")
remotes::install_github("econum/seal.econum", build_vignettes = TRUE)
```

### Usage

TODO

## Getting help

If you encounter a clear bug, please file a minimal reproducible example on [github](https://github.com/econum/seal.econum/issues).
